Title

### 2018-02-03 wfe/request/request-template.tex
Update artifact template.

% LaTeX template for Artifact Evaluation V20180201
%
% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK)
% and Thierry Moreau (University of Washington, USA)
%
% This document was derived from the original Artifact Appendix
% prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK) 
% and Bruce Childers (University of Pittsburgh, USA)
%
% See example of this Artifact Appendix in the CGO'17 paper (with the CK workflow framework):
% https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
%
% (C)opyright 2014-2018
%
% CC BY 4.0 license
%

@@

\begin{abstract}
Summary of work and associated workflow artifact.

Please, specify if you want a public or a private evaluation.
\end{abstract}

@@

\subsection{Technical Description}
{\em Obligatory. Provide a technical description of your novel work, 
or references to your already published work which you are providing an artifact for.}

@@

{\em Obligatory. Use just a few informal keywords in all fields applicable to your artifacts
and remove the rest. This information is needed to find appropriate reviewers and gradually 
unify artifact meta information in Digital Libraries.}

@@

Please, specify which metrics you improve
(execution time, accuracy, power consumption, 
memory usage, device cost, usage cost, etc)

>>>>

% LaTeX template for Artifact Evaluation V20180201
%
% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK)
% and Thierry Moreau (University of Washington, USA)
%
% This document was derived from the original Artifact Appendix
% prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK) 
% and Bruce Childers (University of Pittsburgh, USA)
%
% See an example of this Artifact Appendix in the following CGO 2017 paper
% (with the artifact prepared using the Collective Knowledge framework):
% https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
%
% (C)opyright 2014-2018
%
% CC BY 4.0 license
%

@@

\begin{abstract}
Please provide a summary of work and associated workflow artifact.

Please specify if you would like a public or private evaluation.
\end{abstract}

@@

\subsection{Technical Description}
{\em Obligatory. Provide a technical description of your new work, 
or references to your already published work which you are providing an artifact for.}

@@

{\em Obligatory. Use a few informal keywords in all the fields applicable to your artifacts
and remove the rest. This information is needed to find appropriate reviewers and gradually 
unify artifact meta information in Digital Libraries.}

@@

Please specify which metrics you improve
(execution time, accuracy, power consumption, 
memory usage, device cost, usage cost, etc.)
